---
title: "DecisionTree-ID3-RestaurantFullAnalysis"
author: "Rstudio"
date: "February 3, 2020"
output: html_document
Ref1: https://www.cs.cmu.edu/~cga/ai-course/dtree.pdf 
Ref2: 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}

res=read.csv(file="C:\\Users\\usss\\Google Drive\\IOA\\Academic\\ML\\restaurant_visits.csv")
 
library(FSelector)
library(stringr)

res=res[,-1]
res$Pat = str_trim(res$Pat)

test = res[res$Pat == "Full",]

weights <- information.gain(Wait~., test, unit="log2")
print(weights)

```

```{r}
res=read.csv(file="C:\\Users\\usss\\Google Drive\\IOA\\Academic\\ML\\restaurant_visits.csv",)

library(FSelector)
res=res[,-1]
res
dim(res)

weights <- information.gain(Wait~., res, unit="log2")
print(weights)

subset <- cutoff.k(weights,3)

f <- as.simple.formula(subset, "Wait")
print(f)

```

## -----------------------------------------------
## res$Pat == 'None' is with prob no one will stay
## res$Pat == 'Some' is with prob no one will stay
## Now select only sample that are res$Pat=='Full' to predict further
## -----------------------------------------------

```{r}
res=read.csv(file="C:\\Users\\usss\\Google Drive\\IOA\\Academic\\ML\\restaurant_visits.csv",stringsAsFactors = FALSE)

library(FSelector)
library(dplyr)
res=res[,-1]
names(res)
class(res$Pat)
which(res$Est=='10-30')

res=res[which(res$Pat=='Full'),]



res=filter(res, Pat=="Full") 

res

weights <- information.gain(Wait~., data=res, unit="log2")
print(weights)

```

## ---There are many variables with the same information gain
## ---with equally likely selection
## ---We select the one with alphabetically next - variable 'Est'
## ---In the wait estimate, 60+, no one will stay 100% and 0-10 minutes every one will stay 100%
## ---So we need to resolve 10-30 minutes and 30-60 minutes

```{r}
res=read.csv(file="C:\\Users\\usss\\Google Drive\\IOA\\Academic\\ML\\restaurant_visits.csv") 

library(FSelector)
res=res[,-1]

res=res[res$Pat == 'Full',]
res=res[res$Est == '10-30',]
res   # printing the selected data with the above conditions

weights <- information.gain(Target~., res, unit="log2")

paste("Information gain for the subset where Pat == 'Full' and Est=='10-30'")
print(weights)

```

```{r}
library(rattle)
library(rpart.plot)
library(RColorBrewer)

res=read.csv(file="C:\\Users\\usss\\Google Drive\\IOA\\Academic\\ML\\restaurant_visits.csv") 
res=res[,-1]
mytree <- rpart(
  Target ~ ., 
  data = res, 
  method = "class",
  parms = list(split = 'information'), 
  minsplit = 2, 
  minbucket = 1
)

mytree

# plot mytree
fancyRpartPlot(mytree, caption = NULL)

```

```{r}
### Reading data from google drive directly as a zip file containing a csv

id <- "17m98nQ63WOeWTBAEfdE2iJ0NUQ8WY0IK" # google file ID 
oa1<-read.csv(sprintf("https://docs.google.com/uc?id=%s&export=download", id))
str(oa) 

print(oa)
```

```{r}
### Calculating bits needed to store the information 
### Step2 - Choice of variables to split
 
oa=oa[,-1]
set.seed(43321)
oa$Target=as.factor(oa$Target)
oaRF2=randomForest(Target~., data=oa, ntree=100, proximity=T, mtry=2)
oaRF2
table( oa$Target,predict(oaRF2))
oaRF2
plot(oaRF2)

oaRF3=randomForest(Target~., data=oa, ntree=100, proximity=T, mtry=3)
oaRF3
table( oa$Target,predict(oaRF3))
plot(oaRF3)


oaRF4=randomForest(Target~., data=oa, ntree=100, proximity=T, mtry=4)
oaRF4
table( oa$Target,predict(oaRF4))
oaRF4
plot(oaRF4)



```



```{r}




